---
title: "Theoretical Lot Audits Data Observations"
output: html_document
date: "2025-06-25"
---
<a id="top"></a>

<br>
<nav style="background-color:#f8f9fa; padding: 10px; margin-bottom: 20px; border-bottom: 1px solid #ddd;"> <a href="#data_observation" style="margin-right: 20px;">Data Observations</a> <a href="#other" style="margin-right: 20px;">Other Observations(w/ visuals)</a></nav>
<br>


Loading Data
```{r}
theoretical_lot_audits = read.csv(file = "data/assesment.csv")
```



### **DATA CLEANING**


There are rows where there is a System.Entry.Date and a System.User but nothing in the Adjusted..Pcs column.
<br>
```{r}
head(theoretical_lot_audits[which(theoretical_lot_audits$Adjusted..Pcs == ""), ])
```

This shows that indeed all of the null values in Adjusted.Pcs where there was a System.Entry.Date/ System.User was because the adjustment was 0.
<br>
```{r}
null_adjusted_audits = theoretical_lot_audits[which(theoretical_lot_audits$Adjusted..Pcs == "" & theoretical_lot_audits$System.User != ""), ]

null_adjusted_audits[1:20, ]# first 20 rows

null_adjusted_audits$Initial.Stock.Pcs - null_adjusted_audits$Final.Count.Pcs


```


I'll replace the null values with 0
```{r}
adjusted_pc_null_index = which(theoretical_lot_audits$Adjusted..Pcs == "" & theoretical_lot_audits$System.User != "")

theoretical_lot_audits$Adjusted..Pcs[theoretical_lot_audits$Adjusted..Pcs == "" & theoretical_lot_audits$System.User != ""] = rep(0, 19)

```

This is the new data frame with 0 instead of null values
```{r}
theoretical_lot_audits[1:20, ] # first 20 rows
```

This shows that there is still an issue with the Adjusted.Pcs column as there is a "|" where there should be a number
```{r}
# 
unique(theoretical_lot_audits$Adjusted..Pcs[which(theoretical_lot_audits$Adjusted..Pcs != "")])

```
```{r}
theoretical_lot_audits[which(theoretical_lot_audits$Adjusted..Pcs == "|"), ]

```

Since it should be 0 like the null values lets fix it.
```{r}
# fixed the data entry error
theoretical_lot_audits$Adjusted..Pcs[theoretical_lot_audits$Adjusted..Pcs == "|" & theoretical_lot_audits$System.User != ""] = c(0)

theoretical_lot_audits[which(theoretical_lot_audits$Lot. == "Lot2485"), ]

```

Another Error: Fix data entry error for incorrect system entry date
```{r}
theoretical_lot_audits[which(theoretical_lot_audits$System.Entry.Date == "5/31/0202"), ] 

theoretical_lot_audits$System.Entry.Date[theoretical_lot_audits$System.Entry.Date == "5/31/0202"] = "5/31/2022"

theoretical_lot_audits[2021, ]
```
Would clean but not enough information to.
```{r}
# used excel pivot tables to find errors

# there appears to have been an audit where the admin did not enter their name or the system entry date
theoretical_lot_audits[which(theoretical_lot_audits$System.User == "" & theoretical_lot_audits$Adjusted..Pcs != ""), ]

```

<br>
<a id="data_observation"></a>
<br>

<nav style="background-color:#f8f9fa; padding: 10px; margin-bottom: 20px; border-bottom: 1px solid #ddd;"> <a href="#top" style="margin-right: 20px;">Back To Top</a></nav>


### **DATA OBSERVATIONS**
<br>
<br>

#### **Total Number of  Unique Lots**
<br>
Look for duplicate lots.
```{r}
duplicates = theoretical_lot_audits$Lot.[duplicated(theoretical_lot_audits$Lot.)]

duplicates[1:20] # rest are also null
```

There are 6 repeat lots
```{r}
duplicated_lots = duplicates[which(duplicates != "")]
duplicated_lots
```

**THERE ARE 2562 UNIQUE LOTS**
```{r}
# number of total lots - number of duplicate lots
num_unique_lots = length(theoretical_lot_audits$Lot.[which(theoretical_lot_audits$Lot. != "")]) - length(duplicated_lots)

# number of unique lots
paste("THERE ARE",num_unique_lots, "UNIQUE LOTS")

```

<br>

#### **Unique Lots Audited (# & %)**

<br>
Every audited lot.
```{r}
audited_lots_df = theoretical_lot_audits[which(theoretical_lot_audits$Adjusted..Pcs != ""), ]

audited_lots_df[1:20, ] # first 20 rows
```
Find duplicate audited lots.
```{r}
# duplicate audited lots
audited_duplicates = audited_lots_df$Lot.[duplicated(audited_lots_df$Lot.)]

audited_duplicates
```

**THERE ARE  2463 UNIQUE AUDITED LOTS**

```{r}
num_unique_audited_lots = dim(audited_lots_df)[1] - length(audited_duplicates)
paste("THERE ARE",num_unique_audited_lots, "UNIQUE AUDITED LOTS")
```

**96.14 PERCENT OF UNIQUE LOTS HAVE BEEN AUDITED**
```{r}
# percentage of unique lots audited
percent_audited_unique_lots = (num_unique_audited_lots / num_unique_lots) * 100
paste(round(percent_audited_unique_lots, 2), "PERCENT OF UNIQUE LOTS HAVE BEEN AUDITED")
```


<br>

#### **Unique Lots Remaining to be Audited (# & %)**

<br>

Every lot that isn't audited.
```{r}
not_audited_lots_df = theoretical_lot_audits[which(theoretical_lot_audits$Adjusted..Pcs == "" & theoretical_lot_audits$Lot. != "" ), ]

head(not_audited_lots_df) #shows first 6 rows

```

Shows if there are any duplicate not audited lots.
```{r}

not_audited_duplicates = not_audited_lots_df$Lot.[duplicated(not_audited_lots_df$Lot.)]

not_audited_duplicates

```
**99 LOTS HAVEN'T BEEN AUDITED**
```{r}
# since there are no duplicates we can use just the dimensions of the data frame

# number of unique lots that aren't audited
paste(dim(not_audited_lots_df)[1], "LOTS HAVEN'T BEEN AUDITED" )
```

**3.86 PERCENT OF LOTS HAVENT BEEN AUDITED**
```{r}
# percentage of unique lots not yet audited

paste(round((dim(not_audited_lots_df)[1]  / num_unique_lots) * 100, 2), "PERCENT OF LOTS HAVENT BEEN AUDITED")
```




<br>


#### **Total Adjustments (pcs) (# & %)**

<br>

**THERE ARE 2469 TOTAL ADJUSTMENTS**
```{r}
# this includes duplicate lots since we're looking for total not unique

# total number of adjustments
total_num_adjustments = length(theoretical_lot_audits$Adjusted..Pcs[which(theoretical_lot_audits$Adjusted..Pcs != "")])

paste("THERE ARE",total_num_adjustments, "TOTAL ADJUSTMENTS")
```

**96.14 PERCENT OF LOTS HAVE HAD AN ADJUSTMENT MADE**
```{r}
# where the data stops
last_data_index = which(theoretical_lot_audits$Adjusted..Pcs == "" & theoretical_lot_audits$Lot. == "")[1] - 1


# because of the way that I cleaned my data, percentage adjusted is the same as percentage of lots audited

# percentage of adjustments made
paste(round((total_num_adjustments / dim(theoretical_lot_audits[1:last_data_index, ])[1]) * 100, 2), "PERCENT OF LOTS HAVE HAD AN ADJUSTMENT MADE")

```


```{r, echo=FALSE, eval=FALSE}
# theoretical_lot_audits$Adjusted..Pcs[which(theoretical_lot_audits$Adjusted..Pcs != "")]
# length(theoretical_lot_audits$Adjusted..Pcs[which(theoretical_lot_audits$Adjusted..Pcs != "")])

unique(theoretical_lot_audits$Adjusted..Pcs[which(theoretical_lot_audits$Adjusted..Pcs != "")])

sum(as.numeric((theoretical_lot_audits$Adjusted..Pcs[which(theoretical_lot_audits$Adjusted..Pcs != "")])))


tab_x = table(as.numeric((theoretical_lot_audits$Adjusted..Pcs[which(theoretical_lot_audits$Adjusted..Pcs != "")])))
tab_x
```


<br>
<a id="other"></a>
<br>
<nav style="background-color:#f8f9fa; padding: 10px; margin-bottom: 20px; border-bottom: 1px solid #ddd;"> <a href="#top" style="margin-right: 20px;">Back To Top</a></nav>

### **OTHER INSIGHTS**

```{r}
library(ggplot2)
```

<br>

**REMOVING DUPLICATES FOR THE UPCOMING OBSERVATIONS BECAUSE THEY MESS WITH SUMS OF COLUMNS**
```{r}
theoretical_lot_audits =  theoretical_lot_audits[!duplicated(theoretical_lot_audits[, 3]), ]
```


**THESE 10 STYLES HAD THEIR ENTIRE INVENTORY(INITIAL PCS) USED/MISSING**
```{r, echo=FALSE}
every_style = unique(theoretical_lot_audits$Style.[which(theoretical_lot_audits$Initial.Stock.Pcs != "0")])

every_style_remaining_pcs = c()
every_style_sum_initial = c()

for(i in every_style){
  
  sum_initial_pcs = sum(theoretical_lot_audits$Initial.Stock.Pcs[which(theoretical_lot_audits$Style. == i)])
  
  sum_final_pcs = sum(theoretical_lot_audits$Final.Count.Pcs[which(theoretical_lot_audits$Style. == i)])
  
  every_style_remaining_pcs = append(every_style_remaining_pcs, (sum_final_pcs/ sum_initial_pcs))
  
  every_style_sum_initial = append(every_style_sum_initial, sum_initial_pcs)
  
  

  
}
style_leftover_df = data.frame(style_id = every_style, percent_leftover = every_style_remaining_pcs, initial_amount = every_style_sum_initial)

style_leftover_df[which(style_leftover_df$percent_leftover == 0), ]
```

**THESE 10 STYLES HAD THE MOST INVENTORY(INITIAL PCS) USED/MISSING**
```{r, echo=FALSE}
every_style = unique(theoretical_lot_audits$Style.[which(theoretical_lot_audits$Initial.Stock.Pcs != "0")])

every_style_used_pcs = c()
every_style_sum_initial = c()

for(i in every_style){
  
  sum_initial_pcs = sum(theoretical_lot_audits$Initial.Stock.Pcs[which(theoretical_lot_audits$Style. == i)])
  
  sum_final_pcs = sum(theoretical_lot_audits$Final.Count.Pcs[which(theoretical_lot_audits$Style. == i)])
  
  every_style_used_pcs = append(every_style_used_pcs, (sum_initial_pcs - sum_final_pcs))
  every_style_sum_initial = append(every_style_sum_initial, sum_initial_pcs)
  
  
}
style_used_df = data.frame(style_id = every_style, amount_used_or_missing = every_style_used_pcs, initial_amount = every_style_sum_initial)

top_10_used_styles = style_used_df[order(style_used_df$amount_used_or_missing, decreasing = TRUE), ][1:10, c(1,2)]
top_10_used_styles
```
```{r}
ggplot(top_10_used_styles, aes(x = style_id, y = amount_used_or_missing)) +
  geom_col(fill = "steelblue") + 
  labs(title = "10 Most Used/Missing Style Ids", x = "Style Id", y = "Amount Used/Missing")


```







**LOTS RECEIVED PER YEAR**
(FOR RECIEVE DATES THAT INCLUDED DATES NOT NUMBER CODES)
```{r, echo=FALSE,eval=FALSE}
# 
# theoretical_lot_audits[which(grepl("2022$", theoretical_lot_audits$System.Entry.Date)), ]
# 
# x = unique(substr(theoretical_lot_audits$System.Entry.Date, nchar(theoretical_lot_audits$System.Entry.Date)-3, nchar(theoretical_lot_audits$System.Entry.Date)))
# 
# x




received_dates_without_years = theoretical_lot_audits[which(!grepl("/",theoretical_lot_audits$Received.Date )), ]

received_dates_without_years
# 
# 








```

```{r, echo=FALSE}
received_dates_w_years = theoretical_lot_audits[which(grepl("/",theoretical_lot_audits$Received.Date )), ]

#received_dates_w_years



every_year_unique = unique(substr(received_dates_w_years$Received.Date, nchar(received_dates_w_years$Received.Date)-3, nchar(received_dates_w_years$Received.Date)))

#every_year_unique



num_lots_received = c()
for(i in every_year_unique){
  
  
  all_data_for_year = received_dates_w_years[which(substr(received_dates_w_years$Received.Date, nchar(received_dates_w_years$Received.Date)-3, nchar(received_dates_w_years$Received.Date)) == i ), ]
  
  num_lots_received = append(num_lots_received, length(all_data_for_year$Lot.))
}

lots_per_year_df = data.frame(year = every_year_unique, lots_received = num_lots_received)

lots_per_year_df


```




```{r}
ggplot(lots_per_year_df, aes(x = year, y = lots_received)) +
  geom_col(fill = "steelblue") + 
  labs(title = "Lots Received Per Year", x = "Year", y = "Number of Lots")

```










